WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2021-01-01 Thesis.tex
Fixed comparison table
Added news abbr

\usepackage{setspace}
\usepackage{tabu}
\usepackage[acronym,nopostdot,nonumberlist]{glossaries}
\makeglossaries
\usepackage{import}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{dirtytalk}
\usepackage{tabulary}
\usepackage{multirow}
\usepackage[style=ieee]{biblatex}
\usepackage[titletoc]{appendix}
\usepackage{siunitx}

@@

\acrfull{nwms} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format  %that can be 
ingested by the \acrshort{nwm}. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwms}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containerized applications. Moreover, most of these softwares are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
Therefore, in this research, we propose \acrfull{wdias} that utilizes %modern architectural patterns such as 
microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities. Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
We demonstrate the utility of \acrshort{wdias} using a cloud-based experimental setup and weather-related synthetic workloads.

>>>>

\usepackage{setspace}
\usepackage{tabu}
\usepackage[acronym,nopostdot,nonumberlist]{glossaries}
\makeglossaries
\usepackage{import}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{dirtytalk}
\usepackage{tabulary}
\usepackage{multirow}
\usepackage[style=ieee]{biblatex}
\usepackage[titletoc]{appendix}
\usepackage{siunitx}
\usepackage[misc,geometry]{ifsym} % https://tex.stackexchange.com/a/107112/181545, http://tug.ctan.org/info/symbols/comprehensive/symbols-a4.pdf

@@

\acrfull{nwms} utilize data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before using such multimodal data in a \acrshort{nwm}, it is necessary to transcode data into a format ingested by the \acrshort{nwm}. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and flash floods that require rapid and frequent execution of \acrshort{nwms}. The resulting weather data also need to be accessed by many researchers and third-party applications such as logistic and agricultural insurance firms.
Existing weather data integration systems are based on monolithic or client-server architectures; hence, unable to benefit from novel computational models such as cloud computing and containerized applications. Moreover, most of these softwares are proprietary or closed-source, making it difficult to customize them for an island like Sri Lanka with different weather seasons.
Therefore, in this research, we propose \acrfull{wdias} that utilizes microservices to achieve scalability, high availability, and low-cost operation based on cloud computing. The use of stateless microservices also enables \acrshort{wdias} to add new features on the fly with rollover capabilities. Moreover, \acrshort{wdias} provides a modular framework to integrate data from different sources, export into different formats, and add new functionality by adding extension modules.
We demonstrate the utility of \acrshort{wdias} using a cloud-based experimental setup and weather-related synthetic workloads.

### 2021-01-01 introduction/sec_1-motivation.tex
Added news abbr

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These \acrshort{nwm}s utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwm}s, it is necessary to convert them to a data format that can be ingest by the models. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwm}s.

Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwm}, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work.

@@

Given the above reasons, there is a necessity to develop a WDIA system that could handle large volumes of multimodel data efficiently while providing scalability and high throughput. Moreover, it is desirable to support controlled data sharing with other NWMs and third-party access to enable multiple use cases. Furthermore, such a system should be architectured to benefit from technologies such as cloud computing, microservices, and loosely coupled containerized applications.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These \acrshort{nwms} utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective \acrshort{nwms}, it is necessary to convert them to a data format that can be ingest by the models. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of \acrshort{nwms}.

Weather data processed by a \acrshort{nwm} maybe used by several other \acrshort{nwms}, as well as by many third-party applications and researcher. For example, logistic companies could use the processed data with their data models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on the anticipated weather patterns. Besides, farmers could rely on weather forecasts to plan their work.

@@

Given the above reasons, there is a necessity to develop a WDIA system that could handle large volumes of multimodel data efficiently while providing scalability and high throughput. Moreover, it is desirable to support controlled data sharing with other \acrshort{nwms} and third-party access to enable multiple use cases. Furthermore, such a system should be architectured to benefit from technologies such as cloud computing, microservices, and loosely coupled containerized applications.

### 2021-01-01 lit/sec_1-fews.tex
Added news abbr

Deltares developed \acrshort{fews} \cite{Werner2013TheSystem} in Netherland for operational forecasting agencies. The \acrshort{fews} codebase is not fully open source at the moment. The main objective of a forecasting system is to run multiple NWMs, hydrologic models, and hydrodynamic models which are required for the predictions. This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}. In the model-centric approach, the inputs need to be in the format specific to the model. Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other models. For example, FLO2D creates human-readable text files as output. However, the Delft-FEWS uses a more modular approach, which is easier to integrate new models and update the system for new requirements. Thus, Delft-FEWS is an integration framework or middleware for the models, rather specific model workflow for weather forecasting.

>>>>

Deltares developed \acrshort{fews} \cite{Werner2013TheSystem} in Netherland for operational forecasting agencies. The \acrshort{fews} codebase is not fully open source at the moment. The main objective of a forecasting system is to run multiple \acrshort{nwms}, hydrologic models, and hydrodynamic models which are required for the predictions. This approach is known as a model-centric approach \cite{Werner2005FloodCatchments}. In the model-centric approach, the inputs need to be in the format specific to the model. Also, the outputs produced by the models are specific to the model; hence, difficult to integrate with other models. For example, FLO2D creates human-readable text files as output. However, the Delft-FEWS uses a more modular approach, which is easier to integrate new models and update the system for new requirements. Thus, Delft-FEWS is an integration framework or middleware for the models, rather specific model workflow for weather forecasting.

### 2021-01-01 results/sec_1-test_plan.tex
Added news abbr

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the NWMs. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. Alternatively, most of the grid type data was generated as results of NWMs. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
\end{itemize}

>>>>

The percentage of number of requests per each data type that comes to the system at a given time can be varied depending on the situation. The majority of weather data requests come from weather stations and other observation tools. Then we need to validate and modify those timeseries data and store them as new timeseries that can directly feed into the \acrshort{nwms}. These weather stations can send the weather data at different frequencies with different parameters such as precipitation, temperature, humidity, and wind direction. Most of the timeseries mentioned above are scalar timeseries. When compared to scalar data, parameters such as wind direction are vector timeseries with a lesser percentage of requests. Alternatively, most of the grid type data was generated as results of \acrshort{nwms}. But those grid data produce in less frequency due to the cost of the computer resource to produce results. After considering those factors we came up with 70\% scalar, 20\% vector, and 10\% grid percentage values as the expected requests rate ratios.
As an upper limit of such scenarios while designing the performance testing, it uses the following;
\begin{itemize}
    \item Hourly (24 data points)
    \item Every 30 minutes (48 data points)
    \item Every 15 minutes (96 data points) - One request is equivalent to a set of data points sent by a weather station in 15-minute interval for a single day
\end{itemize}
